Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated

### 2017-03-11 ms_pre_post.Rmd
More edits through discussion on second pass

<!--- I don't know of any review articles or meta-analyses that look at polyandry to avoid inbreeding. At least, none within the last 10 years. --->
<!--- I'm not sure I understand the point of ''tractable systems'' for post-copulatory inbreeding avoidance -- why not just 'species', as with pre-copulatory? --->
<!--- ''However, there is yet no theory ...'' seems a bit off; we don't really use the model to predict what combinations should be favoured by selection or weigh in on the above studies... at least, not in a way that is clear to me (if I'm mistaken -- could there be an example of how predictions in one of the above systems follows from our model?). --->
<!--- What is the difference between 'rationalised' and 'interpreted'? Do these refer to the same thing, and if so, can we get rid of 'rationalised'? --->
<!--- I still think that the end of this paragraph misses the point a bit with regard to how theory is supposed to function. --->

@@

<!--- the 'polyandry and pre-copulatory and post-copulatory inbreeding avoidance' seems technically off. It relies on readers to recognise that 'inbreeding avoidance' only applies to the first two items in the list. I suspect this shouldn't be a problem in practice, but I wonder if there's a better way to word this  --->

<!--- Regarding the removal of 'conceptualise', are we suggesting then that prediction is only or most important thing to predict in the long term, and that we can do it with our model? I'm not sure if I agree with either. --->

@@

All males in the population are assumed to be available for any female to choose. We therefore assume that there is no opportunity cost of male mating such that mating with one female does not reduce a male's availability to mate with any other female. Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.

@@

Each male's value with respect to each focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one. The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male. Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity. A new vector of identical size is then created where each element equals the summation of all earlier position elements in the original vector of $q^{m}_{ij}$ values (such that the first element is zero and last is a number $\leq 1$). Because each element in the vector corresponds to a unique male, a random uniform number between zero and one can identify a female's realised mate. This realisation is enacted by identifying the element in the vector that is closest to, but not less than, the random uniform number. Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$. For polyandrous females that choose multiple mates (i.e., $N_{mates}>1$), mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement. In the unlikely event that a female's $N_{males}$ exceeds the total number of available males, then she simply mates with all males.

@@

The probability that an offspring of a focal female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$. Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$. If the focal female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$. A relative quality ($q^{f}_{ij}$) is then calculated for each male by dividing his $Q^{f}_{ij}$ by the sum of the $Q^{f}_{ij}$ values across all of a female's mates. These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity. As with mate choice, one vector element representing a single male is samplied as weighted by these probabilities to determine paternity. Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.

@@

>>>>

<!--- I don't know of any review articles or meta-analyses that look at polyandry to avoid inbreeding. At least, none within the last 10 years. --->
<!--- I'm not sure I understand the point of ''tractable systems'' for post-copulatory inbreeding avoidance -- why not just 'species', as with pre-copulatory? --->
<!--- ''However, there is yet no theory ...'' seems a bit off; we don't really use the model to predict what combinations should be favoured by selection or weigh in on the above studies... at least, not in a way that is clear to me (if I'm mistaken -- could there be an example of how predictions in one of the above systems follows from our model?). --->
<!--- What is the difference between 'rationalised' and 'interpreted'? Do these refer to the same thing, and if so, can we get rid of 'rationalised'? The word 'rationalised' to me suggests guided reasoning instead of honest interpretation. --->
<!--- I still think that the end of this paragraph misses the point a bit with regard to how theory is supposed to function. --->

@@

<!--- the 'polyandry and pre-copulatory and post-copulatory inbreeding avoidance' seems technically off. It relies on readers to recognise that 'inbreeding avoidance' only applies to the first two items in the list. I suspect this shouldn't be a problem in practice, but I wonder if there's a better way to word this  ---> 
<!--- Regarding the removal of 'conceptualise', are we suggesting then that prediction is only or most important thing to predict in the long term, and that we can do it with our model? I'm not sure if I agree with either. --->

@@

All males in the population are assumed to be available for any female to choose. We therefore assume that there is no opportunity cost of male mating, so mating with one female does not reduce a male's availability to mate with any other female. Individual females mate with their total allotment of $N_{males}$ without replacement, meaning that $N_{males}$ models a female's total number of different mates rather than solely her total number of matings.

@@

Each male's value with respect to a focal female is then divided by the sum of all $Q^{m}_{ij}$ values across all males with respect to that female, thereby assigning each male a relative perceived quality $q^{m}_{ij}$, which is constrained to values between zero and one. The value of $q^{m}_{ij}$ then defines the probability that a focal female mates with the male. Mating is realised by placing each $q^{m}_{ij}$ value into a vector whose elements sum to unity. A new vector of identical size is then created where each element equals the summation of all earlier position elements in the original vector of $q^{m}_{ij}$ values (such that the first element is zero and last is a number $\leq 1$). Because each element in the vector corresponds to a unique male, a random uniform number between zero and one can identify a female's realised mate. This realisation is enacted by identifying the element in the vector that is closest to, but not less than, the random uniform number. Mating is therefore stochastic, and females do not always mate with the male of the highest $q^{m}_{ij}$. For polyandrous females that choose multiple mates (i.e., $N_{mates}>1$), mates are chosen iteratively such that $Q^{m}_{ij}$ and $q^{m}_{ij}$ are re-calculated for each additional mate choice, and with $Q^{m}_{ij}$ and therefore $q^{m}_{ij}$ values of already chosen males set to zero to ensure mate sampling without replacement. In the unlikely event that a female's $N_{males}$ exceeds the total number of available males, then she simply mates with all males.

@@

The probability that an offspring of a focal female $i$ is sired by any one of $i$'s mates $j$ is calculated by assigning a perceived fertilisation quality to each $j$ with respect to $i$, $Q^{f}_{ij}$. Perceived fertilisation quality $Q^{f}_{ij}$ is calculated in the same way as perceived mate quality $Q^{m}_{ij}$, such that if a focal female has a strategy of post-copulatory inbreeding avoidance ($F_{p}<0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = (-F_{p} \times k_{ij} + 1)^{-1}$. If the focal female has strategy of post-copulatory inbreeding preference ($F_{p}>0$), then the perceived quality of male $j$ is $Q^{f}_{ij} = F_{p} \times k_{ij} + 1$. A relative quality ($q^{f}_{ij}$) is then calculated for each male by dividing his $Q^{f}_{ij}$ by the sum of the $Q^{f}_{ij}$ values across all of a female's mates. These $q^{f}_{ij}$ values, which lie between zero and one, define the probability of paternity. As with mate choice, one vector element representing a single male is sampled as weighted by these probabilities to determine paternity. Females produce $n$ offspring, so $q^{f}_{ij}$ values are sampled $n$ times independently and with replacement for each female to determine the realised distribution of sires.

@@

<!--- Something about this 'evolved' and 'evolved back' language just sounds very amateurish -- can't we reframe this in terms of selection? --->
